---
title: "R Exercises"
author: "Scott White"
output:
  html_document:
    code_folding: hide
    toc: true
    toc_depth: 3
---


# Introduction

One of the things people have difficulty with when learning a new programming language is coming up with ways to practice using it. I hope to give some help with this document by compiling a list of useful exercises that people can draw from. These could be useful as part of an R workshop, or even used in a course that uses R where some of the students would like a bit more practice with the language. 

# Exercises

## If statements


## Function creation


## Loops


## Builtin function knowledge

1. Given the vector `x`, how can you check if any of the values are greater than 10?
```{r eval=FALSE}
any(x > 10)
```

2. Return the number of elements in the vecot `x`.
```{r eval = FALSE}
length(x)
```

3. How do you return the structure of an R object `y`?
```{r eval=FALSE}
str(y)
```

4. How do you generate 10 normal variables with mean 5 and standard deviation 3?
```{r eval=FALSE}
rnorm(10, mean = 5, sd = 3)
rnorm(10, 5, 3)
```

